Storing messages with multipartite neural cliques

### 2014-07-18 Articles/article.tex
...

	Previous works (\cite{GriBer20114, GriBer20122}) considered the storage of binary constant weight codewords of weight $1$. We study the case of arbitrary weight. It is convenient to take $\mathcal{A}$ as the set of all binary constant weight codewords of weight $a$, where $a$ is a positive integer which we will call number of activities.

	%Let $\mathcal{M}$ be a set of messages of length $c$ over a finite alphabet $\mathcal{A} = \{1, 2, \hdots, {l \choose a}\}$ (where $a$ is a positive integer) and 
	We set $m = | \mathcal{M} |$.

@@

	States of the network are characterized by which neurons are activated. A message corresponds to one, and only one, state of the network. A message $y$ of length $c$ can be seen as an array $x$ of length $c\dot l$ where for each $j\in [1,c]$, the $j$-th symbol of $y$ denoted $y_j$ is represented by $x[(j-1)l+1\hdots jl]$.\footnote{This is a clustered representation. $x$ is separated in $c$ clusters of $l$ units.} We say the network is in state $x$ if for all $j\in [1, c]$, cluster $j$ in the network follows the activation pattern $x[(j-1)l+1\hdots jl]$.

@@

	Storing a message $y$ in the network amounts to consider the network in state $x$, that is for all $j$ and $k$ such as $1 \le k \le l$ and $1 \le j \le c$, the unit $k$ in the cluster $j$ is activated if and only if $x[(j-1)l+k] = 1$ ; then adding all connections between activated units excepting for units sharing the same cluster. Thus we obtain a multipartite clique between activated units representing a message.% The parameter $a$ describing the number of activated units per cluster will be called number of activities.

	Unit $k$ in cluster $j$ thus corresponds to the index $l = (j-1)c+k$.

@@

	$\tilde{W} = \max_{x\in \mathcal{M}} x x^{\intercal}$ which is the matrix where even edges between units in the same cluster have been added.
	$W$ can now be expressed as :

	$W_{ll'} = \bigg \{
  \begin{tabular}{ccc}
  $0$ & if $\exists j\in [1, c], \, (j-1)c+1 \le l,l' \le jc$ \\
  $\tilde{W}_{ll'}$ & otherwise 
  \end{tabular}
  $

@@

  As taking a maximum is associative and commutative, storing can be done online and is independent of the order of messages.

>>>>

	Previous works (\cite{GriBer20114, GriBer20122}) considered the storage of binary constant weight codewords of weight $1$. We study the case of arbitrary weight. It is convenient to take $\mathcal{A}$ as the set of all binary constant weight codewords of weight $a$, where $a$ is a positive integer parameter which we will call number of activities. We set $m = | \mathcal{M} |$.

	%Let $\mathcal{M}$ be a set of messages of length $c$ over a finite alphabet $\mathcal{A} = \{1, 2, \hdots, {l \choose a}\}$ (where $a$ is a positive integer) and

@@

	States of the network are characterized by which units are activated. A message corresponds to one, and only one, state of the network. A message $y$ of length $c$ can be seen as an array $x$ of length $c\dot l$ where for each $j\in [1,c]$, the $j$-th symbol of $y$ denoted $y_j$ is represented by $x[(j-1)l+1\hdots jl]$.\footnote{This is a clustered representation. $x$ is separated in $c$ clusters of $l$ units.} To sum up thje $k$-th unit in the $j$-th cluster corresponds to the index $l = (j-1)l+k$. We say the network is in state $x$ if for all $j\in [1, c]$ and $k\in [1,l]$, units $k$ in cluster $j$ of the network is active if, and only if, $x[(j-1)l+l] = 1$.

@@

	Storing a message $y$ in the network amounts to consider the network in state $x\,$%, that is for all $j$ and $k$ such as $1 \le k \le l$ and $1 \le j \le c$, the unit $k$ in the cluster $j$ is activated if and only if $x[(j-1)l+k] = 1$ 
	; then adding all connections between activated units excepting for units sharing the same cluster. Thus we obtain a multipartite clique between activated units representing a message.% The parameter $a$ describing the number of activated units per cluster will be called number of activities.

@@

	$\tilde{W} = \max_{x\in \mathcal{M}} x x^{\intercal}$ which is the matrix where even edges between units in the same cluster have been added.
	$W$ can now be expressed as :\vspace*{1mm}

	$W_{ll'} = \bigg \{
  \begin{tabular}{ccc}
  $0$ & if $\exists j\in [1, c], \, (j-1)c+1 \le l,l' \le jc$ \\
  $\tilde{W}_{ll'}$ & otherwise 
  \end{tabular}
  $
  \vspace*{1mm}

@@

  As taking a maximum is associative and commutative, storing can be done online and is independent of the order in which messages are stored.
